---
title: "Beers and Breweries an analysis of US Craft Beers"
author: "Matt Chinchilla, Paritosh Ria"
date: "6/15/2019"
output: html_document
Keep_md: TRUE
---

```{r, message = FALSE }
library(knitr)
library(downloader)
library(dplyr)
library(data.table)
library(ggplot2)
library(webshot)
library(kableExtra)
library(maps)
library(mapdata)
library(tidyverse)
library(stringr)
library(dplyr)
library(viridis)
```


#### Number of Breweries in each state. Note the list is in a scroll box, scroll to see more values.
```{r}
#Read in Brewries.csv file
brewires<-read.csv("Brewries.csv")

#Create a data frame BrewCount with the calculated count of the number of brewries in each state.
BrewCount <- brewires %>% count(brewires$State)

#Update the names of the BrewCount data frame to "State" and "No. of Brewries"
names(BrewCount)<-c("State","No. of Brewires")

#Rearrange the counts in descending order
BrewCount <- arrange(BrewCount, desc(BrewCount$`No. of Brewires`))

#Display the Counts in a styled table
kable(BrewCount) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), fixed_thead = TRUE, full_width = FALSE, position = "left") %>% scroll_box(width = "150%", height = "500px")

```

```{r}
BrewCount1<-BrewCount
BrewCount1<-data.frame(BrewCount1)
head(BrewCount1)

pb<-ggplot(BrewCount ,aes(reorder(BrewCount1$State,-BrewCount1$No..of.Brewires),y=BrewCount1$No..of.Brewires,  fill=BrewCount1$State))+
  geom_bar(stat='identity')+
  theme(text=element_text(size=7),plot.title = element_text(hjust = 0.5),legend.position="none", axis.text.x = element_text(angle = 90))+ 
  ggtitle("Brewires Per State") + 
  labs(x = "State", y = "Brewires per State")

#View Plot
pb
```

#### Merging the Brewires data with the Beers data into a new table "beers_brew" will allow us to do more detailed analysis below are the first and last six values of our new table.
```{r}
#read.csv("beers.csv")
beers<-read.csv("beers.csv")

#Merge beers and Brewieres data frames into beers_brew
beers_brew<-merge(data.frame(beers),data.frame(brewires), by.x = "Brewery_id",by.y="Brew_ID")

#Update Column names
names(beers_brew) <- c("Brewery_ID", "Beer", "Beer_ID", "ABV", "IBU", "Beer_Style", "Ounces", "Brewery_Name", "City", "State")

#First six observation
(head(beers_brew) %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")))
```

```{r}
#Last six observation
tail(beers_brew) %>% kable(row.names = FALSE) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


#### We need to find any null/NA data in our new table the calculation below tells us how many observations are null/NA in each variable.
```{r}
#Total number of NA's in each column
totalna <-colSums(is.na(beers_brew))


#Create table of NA Vales
totalna %>% kable(col.names = c("Number_of_NA")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left")
```

```{r}
#beers_brew
#totalna <-colSums(is.na(beers_brew))
totalna1<-data.frame(totalna)
totalna1 <- cbind(Row.Names = rownames(totalna1), totalna1)
totalna1
colnames(totalna1)<-c("Variables","Number_of_NA")
totalna1

# Add label position
totalna1 <- totalna1 %>%
  #arrange(desc(class)) %>%
  mutate(lab.ypos = cumsum(Number_of_NA) - 0.5*Number_of_NA)
#totalna1

mycols <- c("#868686FF", "#0073C2FF","#0073C2FF","#0073C2FF", "#EFC000FF", "#0073C2FF", "#0073C2FF","#0073C2FF","#0073C2FF","#0073C2FF")

ggplot(totalna1, aes(x = "", y = Number_of_NA, fill =Variables)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
  geom_text(aes(y = lab.ypos, label = Number_of_NA), color = "blue")+
  scale_fill_manual(values = mycols) +
  ggtitle("Number of NA")+
  theme_void()


```


```


#### The median alcholic content for each craft beer in each state and the District of Columbia is in the bar chart below. 
```{r}
#Create a new data frame ABV. 
ABV <- data.frame(beers_brew$Beer_ID, beers_brew$State, beers_brew$ABV)

#Update the column names of ABV to Beer ID, State, and ABV.
names(ABV) <- c("Beer_ID","State","ABV")

#Remove any null values in the new table.
ABV <- na.omit(ABV)

#Create a function to calculate the median.
myFun <- function(x) { median = median(x)}

#Create a new dataframe Median ABV. The function will be used to calculate median ABV per-state.
MedianABV <- as.data.frame.table(tapply(ABV$ABV, ABV$State, myFun))

#Update the column names of MedianABV to State and Median ABV.
names(MedianABV) <- c("State","Median_ABV")

#Build a Bar chart to compare the median ABV per-state
p<-ggplot(MedianABV ,aes(reorder(MedianABV$State,-Median_ABV),Median_ABV, fill= MedianABV$State)) + geom_bar(stat='identity')+ theme(text=element_text(size=10),plot.title = element_text(hjust = 0.5),legend.position="none", axis.text.x = element_text(angle = 90))+ ggtitle("Median ABV Per-State") + labs(x = "State", y = "ABV")

p
```



#### The median IBU bitterness for each craft beer in each state and the District of Columbia is in the bar chart below. Note SD is not listed because the IBU data was not available for the beers in this state.
```{r}
#Create a new data frame IBU. 
IBU <- data.frame(beers_brew$Beer_ID, beers_brew$State, beers_brew$IBU)

#Update the column names of IBU to Beer ID, State, and IBU.
names(IBU) <- c("Beer_ID","State","IBU")

#Remove any null values in the new table.
IBU <- na.omit(IBU)

#Create a function to calculate the median.
myFun <- function(x) { median = median(x)}

#Create a new dataframe Median IBU. The function will be used to calculate median IBU per-state.
MedianIBU <- as.data.frame.table(tapply(IBU$IBU, IBU$State, myFun))

#Update the column names of MedianIBU to State and Median IBU.
names(MedianIBU) <- c("State","Median_IBU")

#Remove SD because it does not have a median value
MedianIBU <- na.omit(MedianIBU)

#Build a Bar chart to compare the median IBU per-state
p1<-ggplot(MedianIBU ,aes(reorder(MedianIBU$State,-Median_IBU),Median_IBU, fill= MedianIBU$State)) + geom_bar(stat='identity')+ theme(text=element_text(size=10),plot.title = element_text(hjust = 0.5),legend.position="none", axis.text.x = element_text(angle = 90))+ ggtitle("Median IBU Per-State") + labs(x = "State", y = "IBU")

p1
```



#### Colorado is the state with the beer with the highest alcohol content in the US. Lee Hill Vol.5 - Belgian Style Quadrupel Ale has an ABV of .128 (13% alcohol content). This beer is prodcuced by Uposlope Brewing Company.
```{r}
#View The row for maximum ABV value (Alcohol content)
beers_brew[which.max(beers_brew$ABV),] %>% kable(row.names = FALSE) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```




#### Orgon is the state with the Bitterest Beer "Bitter Bitch Imperial IPA" this beer is 138 IBU and an American Double/Imperial IPA style. The brewery that produces this beer is Astroria Brewing Company.
```{r}
#View the row with max IBU value (bitterness)
beers_brew[which.max(beers_brew$IBU),] %>% kable(row.names = FALSE) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
 

#### ABV summary stats 
```{r}
#Summarise the ABV variable in the beer_brew table
ABVSummary <- summary(beers_brew$ABV)

#Create table
as.array(ABVSummary) %>% kable(col.names = c("Measure","Value")) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
